Hidden Talents Multiverse Analysis

### 2021-12-21 README.Rmd
fixing scripts - CD revision 1

To reproduce this repository, see [How to reproduce this respository](#repro) below.

@@

1.  `codebooks/`: lists of variable names, labels, and value labels (where applicable).
2.  `data/`: data, stored as an `.Rdata` file and `.csv` files.
3.  `manuscript`: a manuscript written in R markdown for submission to a journal.
4.  `multiverse-objects/`: all `.Rdata` files containing objects necessary for performing multiverse analyses and storing intermediary results.
5.  `scripts/`: R-scripts that read, analyze, and produce all multiverse objects.
6.  `supplement/`: a supplemental text (to be submitted with the manuscript) documenting all secondary analyses in detail.

@@

- `1-multiverse-datasets`: multiverse data sets with each data universe stored in a list. There is one list used for the composites and one list used for all components of each IV.
- `2-primary-analyses`: contain the multiverse of full results and extracted effects for the primary confirmatory and exploratory results
- `3-secondary-analyses`: contain the same objects as above for each set of secondary analyses.

@@

|script|input|output|
|------|-----|------|
|1-data-non-abritrary.R|data1_raw.Rdata|1-raw.csv<br> 2-non_arbitrary.csv<br> 3-composites.csv<br> 4-multiverse_base.csv<br> vars1_raw.csv<br> vars2_non_arbitrary.csv<br> vars3_composites.csv<br> vars4_multiverse_base.csv<br> data2_analysis.Rdata|
|2-primary-multiverse-datasets.R|data2_analysis.Rdata|datalist-agg-ivs.Rdata|
|3-secondary-multiverse-datasets.R|data2_analysis.Rdata|datalist-all-ivs.Rdata|

@@

## How to reproduce this repository {#repro}

@@

1. `2-primary-analyses/1-confirmatory.R`: conducts unpredictability and violence multiverse analyses for attention-shifting and working memory updating.
2. `2-primary-analyses/1-exploratory.R`: conducts poverty multiverse analyses for attention-shifting and working memory updating.
3. `2-primary-analyses/1-extract-effects.R`: extracts and compiles multiverse data for plotting and reporting.
4. `2-primary-analyses/1-bootstrap-setup.R`: sets up bootstrap samples for bootstrapping technique .
5. `2-primary-analyses/1-bootstrap-spec-analysis.R`: runs specification analyses over all bootstrapped samples to obtain overall *p*-values.

@@

1. Set 1
    1. `3-secondary-analyses/set-1/a1-analysis-ses-vio.R`: conducts secondary analysis labeled "Comparing Violence and Poverty Exposure Interactions with Task-Version" in the manuscript
    2. `3-secondary-analyses/set-1/a2-extract-effects.R`: extracts and compiles multiverse data for plotting and reporting for the analysis labeld "Comparing Violence and Poverty Exposure Interactions with Task-Version" in the manuscript.
    3. `3-secondary-analyses/set-1/b1-analysis-ses-components.R`: conducts an analysis of the components of poverty, which is redundant with the secondary analysis labeled "Exploring Components of Adversity Dimensions", which is conducted below in Set 2. 
    4. `3-secondary-analyses/set-1/b2-extract-effects.R`: extracts effects for poverty component multiverse analyses.
2. Set 2
    1. `3-secondary-analyses/set-2/a1-analysis-adversity-components.R`: conducts an analysis of the components of all adversity composites for the secondary analysis labeled "Exploring Components of Adversity Dimensions" (this is an expansion of the above secondary analysis for the components of poverty in Set 1) 
    2. `3-secondary-analyses/set-2/a2-extract-effects.R`: extracts effects for adversity component multiverse analyses.

>>>>

To reproduce this repository, see [How to reproduce this respository](#how-to-reproduce-this-repository) below.

@@

1.  `codebooks/`: lists of variable names, labels, and value labels (where applicable).
2.  `data/`: data, stored as an `.Rdata` file and `.csv` files.
3.  `manuscript/`: a manuscript written in R markdown for submission to a journal.
4.  `multiverse-objects/`: all `.Rdata` files containing objects necessary for performing multiverse analyses and storing intermediary results.
5.  `scripts/`: R-scripts that read, analyze, and produce all multiverse objects.
6.  `supplement/`: a supplemental text (to be submitted with the manuscript) documenting all secondary analyses in detail.

@@

- `1-multiverse-datasets/`: multiverse data sets with each data universe stored in a list. There is one list used for the composites and one list used for all components of each IV.
- `2-primary-analyses/`: contain the multiverse of full results and extracted effects for the primary confirmatory and exploratory results
- `3-secondary-analyses/`: contain the same objects as above for each set of secondary analyses.

@@

@@

## How to reproduce this repository

@@

1. `2-primary-analyses/1-confirmatory.R`: conducts unpredictability and violence multiverse analyses for attention-shifting and working memory updating.
2. `2-primary-analyses/2-exploratory.R`: conducts poverty multiverse analyses for attention-shifting and working memory updating.
3. `2-primary-analyses/3-extract-effects.R`: extracts and compiles multiverse data for plotting and reporting.
4. `2-primary-analyses/4-bootstrap-setup.R`: sets up bootstrap samples for bootstrapping technique .
5. `2-primary-analyses/5-bootstrap-spec-analysis.R`: runs specification analyses over all bootstrapped samples to obtain overall *p*-values.

@@

1. Set 1
    1. `3-secondary-analyses/set-1/a1-analysis-ses-vio.R`: conducts secondary analysis labeled "Comparing Violence and Poverty Exposure Interactions with Task-Version" in the manuscript
    2. `3-secondary-analyses/set-1/a2-extract-effects.R`: extracts and compiles multiverse data for plotting and reporting for the analysis labeled "Comparing Violence and Poverty Exposure Interactions with Task-Version" in the manuscript.
    3. `3-secondary-analyses/set-1/b1-analysis-ses-components.R`: conducts an analysis of the components of poverty, which is redundant with the secondary analysis labeled "Exploring Components of Adversity Dimensions", which is conducted below in Set 2. 
    4. `3-secondary-analyses/set-1/b2-extract-effects.R`: extracts effects for poverty component multiverse analyses.
2. Set 2
    1. `3-secondary-analyses/set-2/a1-analysis-adversity-components.R`: conducts an analysis of the components of all adversity composites for the secondary analysis labeled "Exploring Components of Adversity Dimensions" (this is an expansion of the above secondary analysis for the components of poverty in Set 1) 
    2. `3-secondary-analyses/set-2/a2-extract-effects.R`: extracts effects for adversity component multiverse analyses.

### 2021-12-21 manuscript/manuscript.Rmd
fixing scripts - CD revision 1

\noindent Adversity-exposed youth often perform poorly on standard cognitive tests. However, the hidden talents approach proposes some abilities are enhanced by adversity, especially under ecologically relevant conditions. Sampling 618 adolescents (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r (txt1_sam$non_arb$sex$females/txt1_sam$non_arb$n$total * 100) %>% round(2)`% female; `r (txt1_sam$non_arb$race$non_white/txt1_sam$non_arb$n$total * 100) %>% round(2)`% non-White), we administered two versions of an attention shifting and working memory updating task—one abstract, one ecological. We measured environmental unpredictability, violence, and poverty, and tested adversity × task version interactions. There were no interactions for attention shifting, but there were main effects of unpredictability and violence, indicating improved attention shifting, on average. For working memory updating, violence- and poverty-exposed youth performed worse on the abstract but not the ecological version, equalizing performance. We found no relation between updating and unpredictability.

@@

The current study collected data from `r txt1_sam$raw$n$total` adolescents (*M~age~* = `r txt1_sam$raw$age$mean`, *SD~age~* = `r txt1_sam$raw$age$sd`) from two sources across Salt Lake City, Utah. The first was a middle school and the second were 5 after-school clubs. The middle school sample (seventh and eighth graders, *N* = `r txt1_sam$raw$n$wjms`; `r txt1_sam$raw$sex$wjms$females` females) formed `r (txt1_sam$raw$n$wjms/txt1_sam$raw$n$total * 100) %>% round(2)`% of the total sample and is socioeconomically and ethnically diverse (`r (txt1_sam$raw$race$non_white/txt1_sam$raw$n$total * 100) %>% round(2)`% non-White; `r (txt1_sam$raw$race$hispanic/txt1_sam$raw$n$total * 100) %>% round(2)`% Hispanic). According to school district records, `r (txt1_sam$raw$free_lunch$wjms/txt1_sam$raw$n$wjms * 100) %>% round(2)`% of students were receiving economic assistance based on family income and/or homelessness (i.e., free or reduced-price lunch or fee waivers). The clubs (*N* = `r txt1_sam$raw$n$bgc`; `r txt1_sam$raw$sex$bgc$female` females) contained a wider age range (*M~age~*= `r txt1_sam$raw$age$bgc$mean`, *SD~age~* = `r txt1_sam$raw$age$bgc$sd`). `r (txt1_sam$raw$free_lunch$bgc/txt1_sam$raw$n$bgc * 100) %>% round(2)`% were receiving free or reduced-price lunch and were also ethnically diverse.

We aggregated data from both sources and applied a set of five exclusion criteria. We applied these criteria before inspecting or testing any relations between predictors and outcomes. Specifically, we excluded participants: 1) with incomplete cognitive task data, 2) with apparent cognitive impairments (e.g., head injuries, disabilities, drug use), 3) who missed two or more trap questions, 4) exposed to extreme distractions during the assessment, and 5) who received more than 60 minutes per day of special education services. After exclusions, the final sample contained `r txt1_sam$non_arb$n$total` adolescents (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r txt1_sam$non_arb$sex$females` females; `r (txt1_sam$non_arb$n$wjms/txt1_sam$non_arb$n$total * 100) %>% round(2)`% from the middle school).

>>>>

\noindent Adversity-exposed youth often perform poorly on standard cognitive tests. However, the hidden talents approach proposes some abilities are enhanced by adversity, especially under ecologically relevant conditions. Sampling 618 adolescents (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r (txt1_sam$non_arb$sex$females/txt1_sam$non_arb$n$total * 100) %>% round(2)`% female; `r ((txt1_sam$non_arb$n$total-txt1_sam$non_arb$race$non_white)/txt1_sam$non_arb$n$total * 100) %>% round(2)`% White), we administered two versions of an attention shifting and working memory updating task—one abstract, one ecological. We measured environmental unpredictability, violence, and poverty, and tested adversity × task version interactions. There were no interactions for attention shifting, but there were main effects of unpredictability and violence, indicating improved attention shifting, on average. For working memory updating, violence- and poverty-exposed youth performed worse on the abstract but not the ecological version, equalizing performance. We found no relation between updating and unpredictability.

@@

The current study collected data from `r txt1_sam$raw$n$total` adolescents (*M~age~* = `r txt1_sam$raw$age$mean`, *SD~age~* = `r txt1_sam$raw$age$sd`) from two sources across Salt Lake City, Utah. The first was a middle school and the second were 5 after-school clubs. The middle school sample (seventh and eighth graders, *N* = `r txt1_sam$raw$n$wjms`; `r txt1_sam$raw$sex$wjms$females` females) formed `r (txt1_sam$raw$n$wjms/txt1_sam$raw$n$total * 100) %>% round(2)`% of the total sample and is socioeconomically and ethnically diverse: `r data1_raw %>% filter(race == 1) %>% nrow()` youth identified as Asian, `r data1_raw %>% filter(race == 2) %>%nrow()` as Native American, `r data1_raw %>% filter(race == 3) %>% nrow()` as African American, `r data1_raw %>% filter(race == 4) %>% nrow()` as White, `r data1_raw %>% filter(race == 5) %>% nrow()` as Hispanic, `r data1_raw %>% filter(race == 6)  %>% nrow()` as Pacific Islander, `r data1_raw %>% filter(race == 7) %>% nrow()` with multiple racial identities, and `r data1_raw %>% filter(is.na(race)) %>% nrow()` were missing. According to school district records, `r (txt1_sam$raw$free_lunch$wjms/txt1_sam$raw$n$wjms * 100) %>% round(2)`% of students were receiving economic assistance based on family income and/or homelessness (i.e., free or reduced-price lunch or fee waivers). The clubs (*N* = `r txt1_sam$raw$n$bgc`; `r txt1_sam$raw$sex$bgc$female` females) contained a wider age range (*M~age~*= `r txt1_sam$raw$age$bgc$mean`, *SD~age~* = `r txt1_sam$raw$age$bgc$sd`). `r (txt1_sam$raw$free_lunch$bgc/txt1_sam$raw$n$bgc * 100) %>% round(2)`% were receiving free or reduced-price lunch and were also ethnically diverse.

We aggregated data from both sources and applied a set of five exclusion criteria. We applied these criteria before inspecting or testing any relations between predictors and outcomes. Specifically, we excluded participants: 1) with incomplete cognitive task data, 2) with apparent cognitive impairments (e.g., head injuries, disabilities, drug use), 3) who missed two or more trap questions, 4) exposed to extreme distractions during the assessment, and 5) who received more than 60 minutes per day of special education services. After exclusions, the final sample contained `r txt1_sam$non_arb$n$total` adolescents (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r txt1_sam$non_arb$sex$females` females; `r (txt1_sam$non_arb$n$wjms/txt1_sam$non_arb$n$total * 100) %>% round(2)`% from the middle school). In terms of racial identity, `r data2_non_arbitrary %>% filter(race == 1) %>% nrow()` youth identified as Asian, `r data2_non_arbitrary %>% filter(race == 2) %>%nrow()` as Native American, `r data2_non_arbitrary %>% filter(race == 3) %>% nrow()` as African American, `r data2_non_arbitrary %>% filter(race == 4) %>% nrow()` as White, `r data2_non_arbitrary %>% filter(race == 5) %>% nrow()` as Hispanic, `r data2_non_arbitrary %>% filter(race == 6)  %>% nrow()` as Pacific Islander, `r data2_non_arbitrary %>% filter(race == 7) %>% nrow()` with multiple racial identities, and `r data2_non_arbitrary %>% filter(is.na(race)) %>% nrow()` were missing.

### 2021-12-21 manuscript/manuscript_docx.Rmd
fixing scripts - CD revision 1

---
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: false
    number_sections: false
    keep_tex: true
    extra_dependencies: ["booktabs","longtable"]
geometry: margin=1in
mainfont: Times
fontsize: 12pt
endnote: no
urlcolor: blue
header-includes:
- \usepackage{float}
- \usepackage{siunitx}
- \usepackage[utf8]{inputenc}
- \usepackage[english]{babel}
- \setlength{\parindent}{2em}
- \setlength{\parskip}{0em}
- \linespread{2}
- \usepackage{titlesec}
- \titleformat{\section}[block]{\normalsize\bfseries\filcenter}{}{}{}
- \titleformat{\subsection}[block]{\normalsize\bfseries}{}{}{}
- \titleformat{\subsubsection}[block]{\bfseries\itshape}{}{}{}
- \titlespacing{\section}{0pt}{0pt}{0pt}
- \titlespacing{\subsection}{0pt}{0pt}{0pt}
- \titlespacing{\subsubsection}{0pt}{0pt}{0pt}
- \usepackage{indentfirst}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhf{}
- \fancyhead[R]{\thepage}
- \fancyhead[L]{HIDDEN TALENTS IN CONTEXT}
- \renewcommand\headrulewidth{0pt}
- \usepackage{fixltx2e}
- \usepackage{caption}
- \usepackage{setspace}
- \captionsetup[table]{labelfont={bf},labelformat={default}, labelsep={newline}}
- \captionsetup[figure]{labelfont={bf},labelformat={default}, labelsep={period}}
- \usepackage{lineno}
bibliography: references.bib
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,
  fig.align = "center",
  fig.pos = "!t", 
  out.extra = "",
  fig.show = "asis",
  message = FALSE,
  warning = FALSE
)

library(tidyverse)
library(kableExtra)
library(gt)

load("staged-objects.Rdata")
```

@@

(ref:figure1) Schematic display of the attention shifting and working memory updating tasks: a) abstract attention shifting, b) ecological attention shifting, c) abstract working memory updating, and d) ecological working memory updating.

```{r figure1, fig.cap='(ref:figure1)'}
knitr::include_graphics("figure1.pdf")
```

@@

```{r table1, results='asis'}
table.01.0 %>% 
  kbl(
    align = "lcccccccccc",  
    booktabs = T,
    escape = F,
    caption = "\\emph{Bivariate correlations and descriptive statistics for measures of adversity and their components.}"
  ) %>% 
  add_header_above(c(" ","Unpredictability" = 3, "Violence" = 3, "Poverty" = 4)) %>% 
  kable_styling(latex_options = c("scale_down", "hold_position")) %>% 
  footnote(
    general       = "Column headers denote adversity constructs and rows indicate components. The upper triangle contain sample sizes for each correlation.",
    general_title = "Note:", 
    symbol        = c("p < .05,","p < .01"),
    symbol_manual = c("*", "**"),
    footnote_as_chunk = T,
    title_format = "italic",
    threeparttable = T
  )
```

@@

(ref:figure2) Visualization of multiverse attention shifting results. Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure, b) plots *p*-curves associated with each interaction term, c) plots sorted interaction $\beta$-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect.

```{r figure2, fig.height=7.25, fig.width=6.25, fig.cap='(ref:figure2)'}
fig2
```

@@

```{r table2, results='asis'}
table.02.0 %>% 
  ungroup() %>% 
  mutate(iv = factor(iv, c("Unpredictability","Violence","Poverty"))) %>%
  arrange(dv,iv) %>% 
  select(-dv) %>% 
  mutate(across(.cols = contains("p_percent"), ~ str_replace(.x, "%", "\\\\%"))) %>% 
   kable(
    col.names = c(" ","$\\beta$", "95\\% CI","\\emph{p} (\\%)","\\emph{p}", "$\\beta$", "95\\% CI","\\emph{p} (\\%)","\\emph{p}"),
    booktabs = T,
    escape = F,
    caption = "\\emph{Median standardized effects, 95\\% confidence intervals, percent significant, and bootstrapped p-values for the main effect of adversity and interaction terms for adversity by task version for attention shifting and working memory updating.}"
  ) %>% 
  add_header_above(c(" " = 1, "Main Effect" = 4, "Interaction" = 4)) %>% 
  group_rows(group_label = "Attention Shifting", start_row = 1, end_row = 3) %>% 
  group_rows(group_label = "Working Memory Updating", start_row = 4, end_row = 6) %>% 
  kable_styling(latex_options = "scale_down") %>% 
  footnote(
    general = "The p (%) column reflects the number of analyses that produced p-values < .05 out of all analyses for a given multiverse analyses. The total number of analyses for each measure was 64. Overall p-values were computed using a bootstrapping resampling method and reflect the probability of obtaining an effect size as extreme or more extreme given the median effect is 0.",
    general_title = "Note:", 
    footnote_as_chunk = T,
    title_format = "italic",
    threeparttable = T
  )
```

@@

(ref:figure3) Visualization of multiverse working memory updating results. Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure, b) plots *p*-curves associated with each interaction term, c) plots sorted interaction $\beta$-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect. Proportions of each arbitrary decision with *p*-values \< .05 are indicated on the right side of each specification grid. Blank proportions indicate proportions = 0.

```{r figure3, fig.height=7.25, fig.width=6.25, fig.cap='(ref:figure3)'}
fig3
```

@@

```{r table3, results='asis'}
table.03.0 %>% 
  ungroup() %>%
  mutate(iv = factor(iv, c("Unpredictability","Violence","Poverty"))) %>%
  arrange(dv,iv) %>% 
  select(-dv) %>% 
  mutate(across(.cols = contains("p_percent"), ~ str_replace(.x, "%", "\\\\%"))) %>% 
   kable(
    col.names = c(" ", "\\emph{b} (abs)", "\\emph{p} (\\%)","\\emph{b} (eco)", "\\emph{p} (\\%)", "\\emph{b} (low)", "\\emph{p} (\\%)","\\emph{b} (high)", "\\emph{p} (\\%)"),
    booktabs = T,
    escape = F,
    caption = "\\emph{Median simple effects (unstandardized) and percent significant for task version and adversity for attention shifting and working memory updating.}"
  ) %>% 
  add_header_above(c(" " = 1, "Task Version" = 4, "Adversity Exposure" = 4)) %>% 
  group_rows(group_label = "Attention Shifting", start_row = 1, end_row = 3) %>% 
  group_rows(group_label = "Working Memory Updating", start_row = 4, end_row = 6) %>% 
  kable_styling(latex_options = "scale_down") %>% 
  footnote(
    general = "Simple effects for Task Version reflect the median effect of adversity in for the abstract version (abs) and ecological version (eco). Simple effects for Adversity reflect the effect of task version when adversity-exposure is low (-1 SD) and high (+1 SD). P-values < .05 out of all analyses for a given multiverse analyses. The total number of analyses for each measure was 64.",
    general_title = "Note:", 
    footnote_as_chunk = T,
    title_format = "italic",
    threeparttable = T
  )
```

@@

For working memory updating, there were no interaction between any unpredictability component (perceived or interview-based) and task-version (see SI Figure 10). However, our expanded analysis with violence exposure revealed that interactions obtained with the composite measure were not driven by neighborhood violence but instead by witnessing or involvement in violence (`r secondary1_medians$updating.vio.Fighting.iv_type_z$p_percent %>% str_remove("\\.00")` of interaction *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 11). No interactions were significant with the neighborhood violence component of the violence composite. For poverty exposure, interview-based parental occupational prestige and school-reported economic disadvantage showed some interaction effects (parental education/occupational prestige `r secondary1_medians$updating.ses.Parents.iv_type_z$p_percent` of *ps* \<.05; school coded economic disadvantage `r secondary1_medians$updating.ses.School.iv_type_z$p_percent` of *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 12). Self-reported perceived resource scarcity showed no interaction effects (see SI Table \@ref(tab:table2), SI Table 3, and SI Figure 12).

>>>>

---
bibliography: references.bib
csl: apa.csl
output:
  officedown::rdocx_document:
    reference_docx: reference-doc.docx
    page_margins:
      bottom: 1
      top: 1
      right: 1
      left: 1
      header: .5
      footer: 0
      gutter: 0
    plots:
      align: center
      caption:
        style: Image Caption
        pre: 'Figure '
        sep: '. '
    tables:
      caption:
        style: Table Caption
        pre: 'Table '
        sep: '. '
---

```{r setup, include=FALSE}
# set up chunk options
knitr::opts_chunk$set(
  echo = F,
  fig.align = "center",
  fig.pos = "!t", 
  out.extra = "",
  fig.show = "asis",
  message = FALSE,
  warning = FALSE
)

# load libraries
library(tidyverse)
library(officer)
library(flextable)

# load all data and objects
load("staged-objects.Rdata")

# set up flextable for tables
set_flextable_defaults(
  font.family = "Times", 
  font.size = 10,
  font.color = "black",
  line_spacing = 1,
  padding.bottom = 1, 
  padding.top = 1,
  padding.left = 1,
  padding.right = 1
)
```

@@

```{r figure1, fig.width=6, dpi=600, fig.id = "figure1", fig.cap.style = "Image Caption", fig.cap='Schematic display of the attention shifting and working memory updating tasks: a) abstract attention shifting, b) ecological attention shifting, c) abstract working memory updating, and d) ecological working memory updating.'}
knitr::include_graphics("figure1.pdf")
```

@@

```{r table1, tab.id = "table1", tab.cap.style = "Table Caption", tab.cap="Bivariate correlations and descriptive statistics for measures of adversity and their components."}
table.01.0 %>% 
  add_column(.after = 4,"empty1" = "") %>% 
  add_column(.after = 8,"empty2" = "") %>% 
  flextable() %>%
  width("empty1", width = .2) %>% 
  width("empty2", width = .2) %>% 
  width(j = 1, width = .75) %>% 
  set_header_labels(Variable = "", empty1 = "", empty2 = "") %>% 
  add_header_row(
    values = c(" ", "Unpredictability", " ", "Violence", " ", "Poverty"),
    colwidths = c(1, 3, 1, 3, 1, 4)
  ) %>% 
  border_remove() %>% 
  border(i = 1, j = c("1","2","3","4","5","6","7","8","9","10"), border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 16, border.bottom = fp_border_default(), part = "body") %>% 
  align(i = 1:2, align = "center", part = "header") %>% 
  bold(i = 1:2, part = "header") %>% 
  set_table_properties(width = 1, layout = "autofit") %>% 
  add_footer_row(
    values = " ",
    colwidths = 13
  ) %>% 
  add_footer_row(
    values = " ",
    colwidths = 13
  ) %>% 
    add_footer_row(
    values = " ",
    colwidths = 13
  ) %>% 
  compose(
    i = 1, j = 1, 
    as_paragraph(as_i("Note: "), "Column headers denote adversity constructs and rows indicate components. The upper triangle contain sample sizes for each correlation."), 
    part = "footer"
  ) %>% 
  compose(
    i = 2, j = 1, 
    as_paragraph(as_i("* p "), "< .05, ", as_i("** p "), "< .01"), 
    part = "footer"
  ) 
```

@@

```{r figure2, fig.id = "figure2", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap = "Visualization of multiverse attention shifting results. Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure, b) plots *p*-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect."}
fig2
```

@@

```{r table2, tab.id = "table2", tab.cap.style = "Table Caption", tab.cap = "Median standardized effects, 95% confidence intervals, percent significant, and bootstrapped p-values for the main effect of adversity and interaction terms for adversity by task version for attention shifting and working memory updating."}
table.02.0 %>% 
  ungroup() %>% 
  mutate(iv = factor(iv, c("Unpredictability","Violence","Poverty"))) %>%
  arrange(dv,iv) %>% 
  select(-dv) %>% 
  add_column(.after = 5,"empty1" = "") %>% 
  add_row(.before = 1, "iv" = "Attention Shifting") %>% 
  add_row(.after = 4, "iv" = "Working Memory Updating") %>% 
  flextable() %>% 
  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
  merge_h_range(i = 5, j1 = 1, j2 = 10) %>% 
  bold(i = c(1,5), j = 1) %>% 
  padding(i = c(2:4, 6:8), j = 1, padding.left = 10) %>% 
  width("empty1", width = .2) %>% 
  set_header_labels(iv = "", empty1 = "", ci_main = "95% CI", ci_int = "95% CI") %>% 
  add_header_row(
    values = c(" ", "Main Effect", " ", "Interaction"),
    colwidths = c(1, 4, 1, 4)
  ) %>% 
  compose(i = 2, j = c(2,7), as_paragraph("\U1D6FD"), part = "header") %>% 
  compose(i = 2, j = c(4,9), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
  compose(i = 2, j = c(5,10), as_paragraph(as_i("p")), part = "header") %>% 
  align(i = 1:2, align = "center", part = "header") %>% 
  border_remove() %>% 
  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 8, border.bottom = fp_border_default(), part = "body") %>% 
  bold(i = 1:2, part = "header") %>% 
  set_table_properties(width = 1, layout = "autofit") %>% 
  add_footer_row(
    values = " ",
    colwidths = 10
  ) %>% 
    add_footer_row(
    values = " ",
    colwidths = 10
  ) %>% 
  compose(
    i = 1, j = 1, 
    as_paragraph(as_i("Note: "), "The p (%) column reflects the number of analyses that produced p-values < .05 out of all analyses for a given multiverse analyses. The total number of analyses for each measure was 64. Overall p-values were computed using a bootstrapping resampling method and reflect the probability of obtaining an effect size as extreme or more extreme given the median effect is 0."), 
    part = "footer"
  )
```

@@

```{r figure3, fig.id = "figure3", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap="Visualization of multiverse working memory updating results. Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure, b) plots *p*-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect. Proportions of each arbitrary decision with *p*-values < .05 are indicated on the right side of each specification grid. Blank proportions indicate proportions = 0."}
fig3
```

@@

```{r table3, tab.id = "table3", tab.cap.style = "Table Caption", tab.cap = "Median simple effects (unstandardized) and percent significant for task version and adversity for attention shifting and working memory updating."}
table.03.0 %>% 
  ungroup() %>%
  mutate(iv = factor(iv, c("Unpredictability","Violence","Poverty"))) %>%
  arrange(dv,iv) %>% 
  select(-dv) %>% 
  add_column(.after = 5,"empty1" = "") %>% 
  add_row(.before = 1, "iv" = "Attention Shifting") %>% 
  add_row(.after = 4, "iv" = "Working Memory Updating") %>% 
  flextable() %>% 
  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
  merge_h_range(i = 5, j1 = 1, j2 = 10) %>% 
  bold(i = c(1,5), j = 1) %>% 
  padding(i = c(2:4, 6:8), j = 1, padding.left = 10) %>% 
  width("empty1", width = .2) %>% 
  set_header_labels(iv = "", empty1 = "") %>% 
  add_header_row(
    values = c(" ", "Task Version", " ", "Adversity Exposure"),
    colwidths = c(1, 4, 1, 4)
  ) %>% 
  compose(i = 2, j = c(2), as_paragraph(as_i("b "), "(abstract)"), part = "header") %>% 
  compose(i = 2, j = c(4), as_paragraph(as_i("b "), "(ecological)"), part = "header") %>% 
  compose(i = 2, j = c(7), as_paragraph(as_i("b "), "(low)"), part = "header") %>% 
  compose(i = 2, j = c(9), as_paragraph(as_i("b "), "(high)"), part = "header") %>% 
  compose(i = 2, j = c(3,8), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
  align(i = 1:2, align = "center", part = "header") %>% 
  border_remove() %>% 
  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 8, border.bottom = fp_border_default(), part = "body") %>% 
  bold(i = 1:2, part = "header") %>% 
  fontsize(size = 11, part = "body") %>%
  set_table_properties(width = 1, layout = "autofit") %>% 
  add_footer_row(
    values = " ",
    colwidths = 10
  ) %>% 
    add_footer_row(
    values = " ",
    colwidths = 10
  ) %>% 
  compose(
    i = 1, j = 1, 
    as_paragraph(as_i("Note: "), "Simple effects for Task Version reflect the median effect of adversity in for the abstract version (abstract) and ecological version (ecological). Simple effects for Adversity reflect the effect of task version when adversity-exposure is low (-1 SD) and high (+1 SD). P-values < .05 out of all analyses for a given multiverse analyses. The total number of analyses for each measure was 64."), 
    part = "footer"
  )
```

@@

For working memory updating, there were no interaction between any unpredictability component (perceived or interview-based) and task-version (see SI Figure 10). However, our expanded analysis with violence exposure revealed that interactions obtained with the composite measure were not driven by neighborhood violence but instead by witnessing or involvement in violence (`r secondary1_medians$updating.vio.Fighting.iv_type_z$p_percent %>% str_remove("\\.00")` of interaction *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 11). No interactions were significant with the neighborhood violence component of the violence composite. For poverty exposure, interview-based parental occupational prestige and school-reported economic disadvantage showed some interaction effects (parental education/occupational prestige `r secondary1_medians$updating.ses.Parents.iv_type_z$p_percent` of *ps* \<.05; school coded economic disadvantage `r secondary1_medians$updating.ses.School.iv_type_z$p_percent` of *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 12). Self-reported perceived resource scarcity showed no interaction effects (see SI Table 2, SI Table 3, and SI Figure 12).
